\myfont Implementation and evaluation of register allocation used to translate LLVM-{}- to x86-64

### 2024-01-07 article.tex
Explain the last graphs

\begin{figure}[H]
  \centering
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple8} 
      \caption{Graph}\label{fig:countdown.dot8}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%c1}\\
      \texttt{\%argc}\\
      \texttt{\%argv}\\
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack8}
    \end{subfigure}
    \caption{Push \texttt{\%c1}}
  \end{minipage}%
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple9} 
      \caption{Graph}\label{fig:countdown.dot9}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%argc}\\
      \texttt{\%argv}\\
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack9}
    \end{subfigure}
    \caption{Pop \texttt{\%c1}}
  \end{minipage}%
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple10} 
      \caption{Graph}\label{fig:countdown.dot10}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%argv}\\
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack10}
    \end{subfigure}
    \caption{Pop \texttt{\%argc}}
  \end{minipage}%
\end{figure}

Dolor sit amet badungadong and so on

\begin{figure}[H]
  \centering
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple11} 
      \caption{Graph}\label{fig:countdown.dot11}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack11}
    \end{subfigure}
    \caption{Pop \texttt{\%argv}} 
  \end{minipage}%
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple12} 
      \caption{Graph}\label{fig:countdown.dot12}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \caption{Stack}\label{fig:countdown.stack12} 
    \end{subfigure}
    \caption{Pop \texttt{\%c1}}
  \end{minipage}%
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple8} 
      \caption{Graph}\label{fig:countdown.dot8}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%c1}\\
      \texttt{\%argc}\\
      \texttt{\%argv}\\
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack8}
    \end{subfigure}
    \caption{Push \texttt{\%c1}}\label{fig:countdown8}
  \end{minipage}%
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple9} 
      \caption{Graph}\label{fig:countdown.dot9}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%argc}\\
      \texttt{\%argv}\\
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack9}
    \end{subfigure}
    \caption{Pop \texttt{\%c1}}\label{fig:countdown9}
  \end{minipage}%
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple10} 
      \caption{Graph}\label{fig:countdown.dot10}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%argv}\\
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack10}
    \end{subfigure}
    \caption{Pop \texttt{\%argc}}
  \end{minipage}%
\end{figure}

\noindent As the last variable \texttt{\%c1} is pushed in Figure \ref{fig:countdown8} and an empty graph remains, the process of reconstructing the graph can begin. When popping \texttt{\%c1} in Figure \ref{fig:countdown9}, it can be assigned any of the two colors as it has no neigbors adjacent, so either is chosen. On the other hand, when assigning \texttt{\%argc}, it's only adjacent naighbor \texttt{\%c1} is already assigned red so only blue remains. Likewise, for \texttt{\%argv} and \texttt{\%cn} their only immediately adjacent neighbor of \texttt{\%argc} causes them to be assigned red as can be seen on Figure \ref{fig:countdown11} and \ref{fig:countdown12}.

\begin{figure}[H]
  \centering
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple11} 
      \caption{Graph}\label{fig:countdown.dot11}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \centering
      \texttt{\%cn}
      \vspace{0.5em}
      \caption{Stack}\label{fig:countdown.stack11}
    \end{subfigure}
    \caption{Pop \texttt{\%argv}} \label{fig:countdown11}
  \end{minipage}%
  \begin{minipage}[c]{0.32\linewidth}
    \begin{subfigure}[b]{0.70\textwidth}
      \includesvg[height=6em]{countdown.simple12} 
      \caption{Graph}\label{fig:countdown.dot12}
    \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
      \caption{Stack}\label{fig:countdown.stack12} 
    \end{subfigure}
    \caption{Pop \texttt{\%c1}}\label{fig:countdown12} 
  \end{minipage}%
\end{figure}
